\addcontentsline{toc}{chapter}{Bibliographie}

\begin{thebibliography}{1}

\bibitem{Agrachev}
\newblock A.~A. Agrachev \& Y.~L. Sachkov,
\newblock \emph{Control theory from the geometric viewpoint}, vol~\textbf{87} of \emph{Encyclopaedia of Mathematical Sciences},
\newblock Springer-Verlag, Berlin (2004), 412 pages.

\bibitem{Arnold}
\newblock V.~Arnold, 
\newblock \emph{\'Equations diff\'erentielles ordinaires},
\newblock MIR, Moscou (1974).

%\bibitem{BonnardCaillau}
%\newblock B.~Bonnard \& J.-B.~Caillau, 
%\newblock \emph{Introduction to nonlinear optimal control},
%\newblock Advanced topics in control systems theory, 1-60, Lecture Notes in Control and Inform. Sci. 328, Springer, 2006.

\bibitem{Brezis}
\newblock H.~Brezis, 
\newblock \emph{Analyse fonctionnelle : th\'eorie et applications},
\newblock Dunod, Paris, 1999, 593 pages.

\bibitem{Cesari}
\newblock L.~Cesari,
\newblock \emph{Optimization-theory and applications: problems with ordinary differential equations},
                vol~17 of \emph{Applications of mathematics},
\newblock Springer-Verlag, New York, 1983, 542 pages.

\bibitem{Cots}
\newblock O.~Cots,
\newblock {\em {Contr\^ole optimal g\'eom\'etrique : m\'ethodes homotopiques et applications}}.
\newblock Phd thesis, Institut Math\'ematiques de Bourgogne, Dijon, France, 2012.

\bibitem{Demailly2006}
\newblock J.~Demailly,
\newblock \emph{Analyse num{\'e}rique et {\'e}quations diff{\'e}rentielles},
\newblock Collection Grenoble Sciences. EDP Sciences (2006).

\bibitem{Gergaud}
\newblock J.~Gergaud,
\newblock \emph{\'Equations diff\'erentielles ordinaires},
\newblock \href{http://gergaud.perso.enseeiht.fr/teaching/edo/edo_utf8.pdf}{pdf}.

\bibitem{Jean}
\newblock F.~Jean,
\newblock \emph{Syst\`emes dynamiques : Stabilit\'e et Commande},
\newblock \href{http://perso.ensta-paristech.fr/~fjean/Cours_enligne/AO102.pdf}{pdf}.

\bibitem{MaurerRayleigh}
\newblock H. Maurer \& D. Augustin,
\newblock \emph{Second order sufficient conditions and sensitivity analysis for the controlled Rayleigh problem},
\newblock in Parametric Optimization and Related Topics, IV: 15–55, J. Guddat, Ed. et al. Frankfurt, Germany: Peter Lang Publishing, 1997.

\bibitem{Pansu}
\newblock P.~Pansu,
\newblock \emph{Cours de G\'eom\'etrie Diff\'erentielle, chapitre 1, calcul des variations},
\newblock \href{http://www.math.u-psud.fr/\%7Epansu/web_dea/chapitre1.pdf}{pdf}.

\bibitem{Pontryagin}
\newblock L.~S. Pontryagin, V.~G. Boltyanski{\u\i}, R.~V. Gamkrelidze \& E.~F. Mishchenko,
\newblock \emph{Matematicheskaya teoriya optimalnykh protsessov},
\newblock ``Nauka'', Moscow, fourth edition (1983).

\bibitem{TrelatRayleigh}
\newblock C.~Silva \& E.~Tr{\'e}lat,
\newblock \emph{Smooth regularization of bang-bang optimal control problems},
\newblock IEEE Trans. Automat. Control, \textbf{55} (2010), no~11, 2488--2499.

\bibitem{Sontag}
\newblock E. D. Sontag,
\newblock \emph{Mathematical control theory: deterministic systems},
\newblock Springer-Verlag New York, Inc., New York, NY, USA, 1990.
\newblock \href{http://www.math.rutgers.edu/~sontag/FTP_DIR/sontag_mathematical_control_theory_springer98.pdf}{pdf}.

\bibitem{Trelat}
\newblock E.~Tr{\'e}lat,
\newblock \emph{Contr\^ole optimal\NoAutoSpaceBeforeFDP: th\'eorie et applications},
\newblock \href{https://www.ljll.math.upmc.fr/trelat/fichiers/livreopt.pdf}{pdf}.

\bibitem{WagschalDI}
\newblock C.~Wagschal,
\newblock \emph{D\'erivation, int\'egration},
\newblock Hermann, 1999.

\end{thebibliography}
